---
title: "Aspen Comparison Analysis"
author: "Marina"
date: '2022-05-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

This experiment is to test the simulation's efficacy at replicating a simple unit cell of a mixture of gases without adsorbents with experimental data. For nature data we're using the back-end experimental data in Aspen thermodynamic simulation software. To set up this experiment we collected a range of y_co, P, and T and performed a GCMC run for each unique set. The Peng Robinson equation of state is also used here for comparison

# Setup

## Packages and Modules

```{r}
suppressPackageStartupMessages({
  library( tidyverse )
  library( data.table )
  library(glue)
})

getwd()
source( "./reference_data/pr.R")
```

## Pull and Combine Aspen Data

```{r}
allFiles <- list.files("reference_data/")

aspenFiles <- allFiles[ grepl( pattern = "CO2-CH4", allFiles)]

aspenData <- lapply( aspenFiles, function( filename ){
  
  dataChunk <- fread( paste0("reference_data/", filename), skip = 1)
  
  return( dataChunk )
  
}) %>%
  bind_rows()


aspenData <- aspenData  %>% 
  mutate(
    yco = round( `Mole fraction CO2`, 1),
    t_c = round( `Temperature (K)` - 273.15, 1 ),
    p_bar = round(`Pressure (N/sqm)`*10**(-5), 1),
    rhoco = yco*`Density (kg/cum)`/44.01,
    rhome = (1-yco)*`Density (kg/cum)`/16.04,
    source = "Aspen"
  )

aspenData %>% head()
```

## Pull and Combine GCMC Experimental Data

```{r}
homeDir <-"./aspen_comparison/"

combineRunData <- function( dataDir, expListFile ){
  
  dataFiles <- list.files(dataDir)
  expList <- fread(  expListFile )
  
  # all the raw data
  rawDataTable <- lapply( dataFiles, function(file){
    
    exp <- str_remove( file, pattern = ".csv")
    
    expInputs <- expList %>%
      filter( exp == !!exp )
    
    expOutputs <- fread( paste0( dataDir, file ) )
    
    
    expData <- bind_cols(expInputs, expOutputs) %>%
      mutate( iter = 1:n() )
    
    return( expData )
    
  }) %>% bind_rows
  
  return( rawDataTable )
}

aspenRunData <- combineRunData(
  paste0(homeDir, "data/"),
  paste0(homeDir, "aspen_comparison.csv")
) %>%
  mutate(
    rhocov = rhocov*10000/6.02,
    rhomev = rhomev*10000/6.02
  )

aspenRunData %>% head()
```

## Combine the 3 Sources (Aspen, GCMC, pr)

```{r}
R = 0.0831446261815324 #[L bar/K mol]
comparisonData <- aspenData %>%
  filter( t_c < 80) %>%
  filter( t_c >= 30) %>%
  filter( p_bar < 250 ) %>%
  select( yco, t_c, p_bar, rhoco, rhome) %>%
  left_join(
    aspenRunData %>%
      select( yco, t_c, p_bar, Pv, Env, rhocov, rhomev ),
    by = c("yco", "t_c", "p_bar")
  ) %>%
  rowwise() %>%
  mutate(
    z_pr = PR_Zmix(p_bar, t_c + 273.15, yco ),
    rho_pr = p_bar/(z_pr*R*(t_c+273.15)), #[mol/L]
    rhoco_pr = yco*rho_pr,
    rhome_pr = (1-yco)*rho_pr
  )

comparisonDataFull <- aspenData %>%
  select( yco, t_c, p_bar, rhoco, rhome) %>%
  left_join(
    aspenRunData %>%
      select( yco, t_c, p_bar, Pv, Env, rhocov, rhomev ),
    by = c("yco", "t_c", "p_bar")
  ) %>%
  rowwise() %>%
  mutate(
    z_pr = PR_Zmix(p_bar, t_c + 273.15, yco ),
    rho_pr = p_bar/(z_pr*R*(t_c+273.15)), #[mol/L]
    rhoco_pr = yco*rho_pr,
    rhome_pr = (1-yco)*rho_pr
  )

theme_set(
  theme_light()
)

comparisonData %>% glimpse()
comparisonDataFull %>% glimpse()
```

# Focused Dataset

```{r}
ggplot( comparisonData ) +
  geom_point(
    aes( x = yco, y = p_bar, col = t_c )
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Span of provided data from Aspen") +
  labs(
    x = "Mole Fraction CO2",
    y = "Reservoir Pressure [bar]",
    col = "Temperature [C]"
  )
```

Here is the range of data used within the bounds of 30 to 80 \*C and under 200 bar. While not completely representative across a range of values, it can serve as a quick glance of our simulation's effectiveness.

## Mole Fraction

```{r}
ggplot( comparisonData ) +
  geom_point(
    aes( x = yco, y = rhocov/(rhocov + rhomev), col = t_c ),
    alpha = 0.2
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Mole Fraction Deviation") +
  labs(
    x = "Reservoir Mole Fraction CO2",
    y = "Simulated Mole Fraction CO2",
    col = "Temperature [C]"
  )

ggplot( comparisonData ) +
  geom_point(
    aes( x = yco, y = rhocov/(rhocov + rhomev), col = p_bar ),
    alpha = 0.2
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Mole Fraction Deviation") +
  labs(
    x = "Reservoir Mole Fraction CO2",
    y = "Simulated Mole Fraction CO2",
    col = "Pressure [bar]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = yco, y = yco - rhocov/(rhocov + rhomev), col = t_c )
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Mole Fraction Deviation (recentered)") +
  labs(
    x = "Reservoir Mole Fraction CO2",
    y = "Simulation Mole Fraction CO2",
    col = "Temperature [C]"
  )

ggplot( comparisonData ) +
  geom_point(
    aes( x = yco, y = yco - rhocov/(rhocov + rhomev), col = p_bar )
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Mole Fraction Deviation (recentered)") +
  labs(
    x = "Reservoir Mole Fraction CO2",
    y = "Simulation Mole Fraction CO2",
    col = "Pressure [bar]"
  )
```

This plot demonstrates the mole fraction difference between reservoir and unit cell. Since there is no adsorbent, there should be no difference between the two and any consistent bias suggests an issue with the simulation's accuracy. Unfortunately due to the available data we don't have much to go on here. While there is a suggestion of an overestimation of CO2 in simulation at higher Mole fractions of CO2, there isn't enough of a range of data to confirm.

## Simulation Pressure

```{r}
ggplot( comparisonData ) +
  geom_point(
    aes( x = p_bar, y = Pv, col = yco ),
    alpha = 1
  ) +
  geom_line(
    aes( x = p_bar, y = p_bar)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Pressure Simulation Integrity") +
  labs(
    x = "Reservoir Pressure [bar]",
    y = "Simulation Pressure [bar]",
    col = "Mol. Frac CO2"
  )

ggplot( comparisonData ) +
  geom_point(
    aes( x = p_bar, y = Pv, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = p_bar, y = p_bar)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Pressure Simulation Integrity") +
  labs(
    x = "Reservoir Pressure [bar]",
    y = "Simulation Pressure [bar]",
    col = "Temp [C]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = p_bar, y = Pv - p_bar, col = yco ),
    alpha = 1
  ) +
  geom_hline( yintercept = 0 ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Pressure Simulation Integrity") +
  labs(
    x = "Reservoir Pressure [bar]",
    y = "Pressure Difference [bar]",
    col = "Mol. Frac CO2"
  )

ggplot( comparisonData ) +
  geom_point(
    aes( x = p_bar, y = Pv - p_bar, col = t_c ),
    alpha = 1
  ) +
  geom_hline( yintercept = 0 ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Pressure Simulation Integrity") +
  labs(
    x = "Reservoir Pressure [bar]",
    y = "Pressure Difference [bar]",
    col = "Temp [C]"
  )
```

These plots demonstrate the differences in pressure between the reservoir (Aspen) and the unit cell (GCMC). In a perfectly working simulation, these values would be the same as there are no adsorbents to impact the sum of forces on the particles. As shown in the difference plots, the simulation is consistently representing lower pressures in the unit cell across all pressures. The difference in pressure gets worse at higher pressures and at higher temperatures.

Hypothesis: I suspect the difference is due to a mismatch in calculated chemical potential by PR as an input to the system and/or a misrepresentation of CO2's Lennard-Jones force field. A higher temp/pressure means more particles in the system for the effect of CO2 discrepancy to take place.

## Density Aspen vs GCMC

```{r}
#### CO2 Aspen v GCMC ####
ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco, y = rhocov, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Temp [C]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco, y = rhocov, col = p_bar ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Pressure [bar]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco, y = rhocov, col = yco ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Mol. Frac CO2"
  )




#### CH4 Aspen v GCMC ####
ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome, y = rhomev, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Temp [C]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome, y = rhomev, col = p_bar ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Pressure [bar]"
  )



ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome, y = rhomev, col = (1-yco) ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "Simulation Density CH4 [mol/L]",
    col = "Mol. Frac CH4"
  )
```

Contrary to the single component comparison results, the CO2 partial densities show no significant bias away from experimental Aspen results. However, there is a clear discrepancy in the CH4 results where the simulation is significantly under-representing the density. The issue gets worse the less CH4 in the system there is. This provides some evidence away from CO2 LJ parameters being the critical issue, although the issue does get worse with more CO2.

## Density Aspen vs PR

```{r}
#### CO2 Aspen v PR ####
ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco, y = rhoco_pr, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "PR Density CO2 [mol/L]",
    col = "Temp [C]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco, y = rhoco_pr, col = p_bar ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "PR Density CO2 [mol/L]",
    col = "Pressure [bar]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco, y = rhoco_pr, col = yco ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "PR Density CO2 [mol/L]",
    col = "Mol. Frac CO2"
  )



#### CH4 Aspen v PR ####
ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome, y = rhome_pr, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "PR Density CH4 [mol/L]",
    col = "Temp [C]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome, y = rhome_pr, col = p_bar ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "PR Density CH4 [mol/L]",
    col = "Pressure [bar]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome, y = rhome_pr, col = (1-yco) ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "PR Density CH4 [mol/L]",
    col = "Mol. Frac CH4"
  )
```

Unexpectedly, the PR results are showing a very same bias away from Aspen experimental data as the gcmc results. This suggests that my chemical potential of the reservoir Equation of State struggles to capture the gas non-ideality in this temperature and pressure range.

## Density GCMC vs PR

```{r}
ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco_pr, y = rhocov, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco_pr, y = rhoco_pr)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "PR Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Temp [C]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco_pr, y = rhocov, col = p_bar ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco_pr, y = rhoco_pr)
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "PR Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Pressure [bar]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhoco_pr, y = rhocov, col = yco ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco_pr, y = rhoco_pr)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "PR Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Mol. Frac CO2"
  )



ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome_pr, y = rhomev, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome_pr, y = rhome_pr)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Component Density Comparison") +
  labs(
    y = "Simulation Density CH4 [mol/L]",
    x = "PR Density CH4 [mol/L]",
    col = "Temp [C]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome_pr, y = rhomev, col = p_bar ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome_pr, y = rhome_pr)
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Component Density Comparison") +
  labs(
    y = "Simulation Density CH4 [mol/L]",
    x = "PR Density CH4 [mol/L]",
    col = "Pressure [bar]"
  )


ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome_pr, y = rhomev, col = (1-yco) ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome_pr, y = rhome_pr)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Component Density Comparison") +
  labs(
    y = "Simluation Density CH4 [mol/L]",
    x = "PR Density CH4 [mol/L]",
    col = "Mol. Frac CH4"
  )
```

As indicated in the Aspen vs PR comparison, the PR and gcmc are in relative accordance. While PR is used as an input into this model, this is only for determination of chemical potential of the reservoir given y, T, and P. This wouldn't influence things like specific density beyond chemical potential's influence.

Next steps:

1.  Investigate PR as an EOS when comparing to gas mixtures in this range
2.  Find more mixture data to compare to, ideally with the full range of y, T, P represented
3.  Investigate other Lennard-Jones parameters and pick the best.

# Full Dataset

```{r}
ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = yco, y = p_bar, col = t_c )
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Span of provided data from Aspen") +
  labs(
    x = "Mole Fraction CO2",
    y = "Reservoir Pressure [bar]",
    col = "Temperature [C]"
  )


ggplot( 
    comparisonDataFull %>%
      filter( yco == 0.5 ) 
  ) + 
  geom_point(
    aes( x = p_bar, y = rhoco, col = t_c)
  ) +
  geom_point(
    aes(x = p_bar, y = rhocov, col = t_c ), shape = 5
  ) +
  
```

## Mole Fraction

```{r}
ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = yco, y = rhocov/(rhocov + rhomev), col = t_c ),
    alpha = 0.2
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Mole Fraction Deviation") +
  labs(
    x = "Reservoir Mole Fraction CO2",
    y = "Simulated Mole Fraction CO2",
    col = "Temperature [C]"
  )

ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = yco, y = rhocov/(rhocov + rhomev), col = p_bar ),
    alpha = 0.2
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Mole Fraction Deviation") +
  labs(
    x = "Reservoir Mole Fraction CO2",
    y = "Simulated Mole Fraction CO2",
    col = "Pressure [bar]"
  )


ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = yco, y = yco - rhocov/(rhocov + rhomev), col = t_c )
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Mole Fraction Deviation (recentered)") +
  labs(
    x = "Reservoir Mole Fraction CO2",
    y = "Simulation Mole Fraction CO2",
    col = "Temperature [C]"
  )

ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = yco, y = yco - rhocov/(rhocov + rhomev), col = p_bar )
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Mole Fraction Deviation (recentered)") +
  labs(
    x = "Reservoir Mole Fraction CO2",
    y = "Simulation Mole Fraction CO2",
    col = "Pressure [bar]"
  )
```

## Simulation Pressure

```{r}
ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = p_bar, y = Pv, col = yco ),
    alpha = 1
  ) +
  geom_line(
    aes( x = p_bar, y = p_bar)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Pressure Simulation Integrity") +
  labs(
    x = "Reservoir Pressure [bar]",
    y = "Simulation Pressure [bar]",
    col = "Mol. Frac CO2"
  )

ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = p_bar, y = Pv, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = p_bar, y = p_bar)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Pressure Simulation Integrity") +
  labs(
    x = "Reservoir Pressure [bar]",
    y = "Simulation Pressure [bar]",
    col = "Temp [C]"
  )


ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = p_bar, y = Pv - p_bar, col = yco ),
    alpha = 1
  ) +
  geom_hline( yintercept = 0 ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Pressure Simulation Integrity") +
  labs(
    x = "Reservoir Pressure [bar]",
    y = "Pressure Difference [bar]",
    col = "Mol. Frac CO2"
  )

ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = p_bar, y = Pv - p_bar, col = t_c ),
    alpha = 1
  ) +
  geom_hline( yintercept = 0 ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Pressure Simulation Integrity") +
  labs(
    x = "Reservoir Pressure [bar]",
    y = "Pressure Difference [bar]",
    col = "Temp [C]"
  )
```

## Density Aspen vs GCMC

### CO2

```{r}
#### CO2 Aspen v GCMC ####
ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = rhoco, y = rhocov, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Temp [C]"
  )


ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = rhoco, y = rhocov, col = p_bar ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Pressure [bar]"
  )


ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = rhoco, y = rhocov, col = yco ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhoco, y = rhoco)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CO2 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Mol. Frac CO2"
  )

```

### CH4

```{r}
#### CH4 Aspen v GCMC ####
ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = rhome, y = rhomev, col = t_c ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "red") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Temp [C]"
  )


ggplot( comparisonDataFull ) +
  geom_point(
    aes( x = rhome, y = rhomev, col = p_bar ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "green") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "Simulation Density CO2 [mol/L]",
    col = "Pressure [bar]"
  )



ggplot( comparisonData ) +
  geom_point(
    aes( x = rhome, y = rhomev, col = (1-yco) ),
    alpha = 1
  ) +
  geom_line(
    aes( x = rhome, y = rhome)
  ) +
  scale_color_gradient(low = "blue", high = "yellow") +
  ggtitle("Component Density Comparison") +
  labs(
    x = "Aspen Density CH4 [mol/L]",
    y = "Simulation Density CH4 [mol/L]",
    col = "Mol. Frac CH4"
  )
```
